---
title: "MetaLINCSOutput"
subtitle: "Created based on input data."
author: "Maybe later"
output: 
  html_document: 
    toc: yes
    toc_depth: 2
    theme: united
    highlight: tango
    number_sections: true
    toc_float:
      collapsed: false
      smooth_scroll: false
params:
    out1: out1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- make a block to set working directory and print it-->
```{r dumb}
cat("Current working directory: ",getwd(),"\n")
setwd("/root/results")
cat("Current working directory: ",getwd(),"\n")
```

# Success

Thanks for running MetaLINCS on Latch! This is your summary.

Can write more here for intro....

```{r}

#This code chunk is empty, other than this comment

```

When pound signs (hashtags) are outside of code blogs, they indicate headers. # Largest Header. ## Smaller header. ### Even Smaller Header. You can see these when this file is knit (more on that later)

Optional: find the "explore document outline" option to see how headers automatically sort into an interactive document outline in Rmarkdown.

Maybe have packages here?
  

## Install packages 
(done only once) rn idk why this is not small header

There are well over 10,000 packages people have created that allow you to do different things with R -- and in different ways. (R generally has many different ways of doing the same thing.)

You will probably need the below packages on some of the assignments, so you might as well install them now. Don't worry about what they do right now.

# Preprocessing

```{r, echo=FALSE}
print(out1)
```

<!-- # install.packages("glmnet")
# install.packages("ggplot2")
# # devtools::install_github("xia-lab/MetaboAnalystR", build = TRUE, build_vignettes = TRUE, build_manual =T)
# install.packages("scales")
# install.packages("pheatmap")
# install.packages("tidyverse")
# install.packages("reshape")
# install.packages("magrittr")
# install.packages("ggpubr")
# install.packages("ggplot2")
# install.packages("lsmeans")
# install.packages("multcomp")
# install.packages("ggplot2")
# install.packages("corrplot")
# install.packages("Hmisc")
# BiocManager::install("ComplexHeatmap")
# install.packages("circlize")

# library(glmnet)
# library(ggplot2)
# #library(MetaboAnalystR) # It will take long time to install, you can comment this line 
# library("scales")
# library(pheatmap)
# library(tidyverse)
# library(reshape2)
# library(magrittr)
# library("ggpubr")
# library(lsmeans)
# library(multcomp)
# library(corrplot)
# library("Hmisc")
# library(ComplexHeatmap)
# library(circlize)



# metabolomics_meta= read.csv("metabolomics_meta_R21_SOV.csv")   
# samples_meta= read.csv("samples_meta_R21_SOV.csv",na.strings=c("NA","NaN", ""))       # samples unique ids is the sample id   
# metabolomics_data= read.csv("metabolomics_data_R21_SOV.csv",check.names=F,row.names=1)  # metabolomics id is the comp id
# dim(metabolomics_data)
# dim(metabolomics_meta)
# dim(samples_meta)
# print("********************Metabolomics data")
# head(metabolomics_data)
# print("********************Metaboloites annotation")
# head(metabolomics_meta)
# print("********************Samples annotation")
# head(samples_meta)

# options(echo=FALSE) #do I need this?
args <- commandArgs(trailingOnly = TRUE)
print(args)

#do the file building here, to html
metabolomics_meta= args[1] # hve to open the file here, otherwise it will not work
samples_meta= args[2]
metabolomics_data = args[3]

int.mat <- metabolomics_data
rowNms <- rownames(int.mat)
colNms <- colnames(int.mat)
naNms <- sum(is.na(int.mat))
num.mat <- suppressWarnings(apply(int.mat, 2, as.numeric))
if (sum(is.na(num.mat)) > naNms) {
    num.mat <- apply(int.mat, 2, function(x) as.numeric(gsub(",", "", x)))
    if (sum(is.na(num.mat)) > naNms) {
        print("Non-numeric values were found and replaced by NA.")
    }
    else {
        print("All data values are numeric.")
    }
} 
 -->
